R Notebook

### 2017-03-31 doc/RMD/MLG-distribution.Rmd
add ggraph

```{r}
library('tidyverse')
library('assertr')
library('poppr')
library('igraph')
```

@@

```{r, fig.width = 10, fig.height = 10}
psize <- table(pop(clonecorrect(dat, ~Region)))
pops <- crosses %>%
  mutate_if(is.factor, as.character) %>%
  group_by(Population) %>%
  summarize(MLG = list(as.character(MLG))) %>%
  group_by(Population) %>%
  mutate(size = psize[unlist(Population)]) %>%
  mutate(n_private = size - lengths(MLG)) %>%
  mutate(interactions = list(pg$Population[pg$MLG %in% unlist(MLG)] %>% 
                               setNames(unlist(MLG)) %>% 
                               bind_rows(.id = "MLG") %>% 
                               distinct() %>%
                               filter(Population == from | Population == to))) %>%
  mutate(graph = map(interactions, ~select(.x, from, to, MLG) %>% 
                       rename(name = MLG) %>% 
                       graph_from_data_frame(directed = FALSE)))
pops
par(mfrow = c(3, 4))

@@

glayout_df <- glayout %>% 
  data.frame %>% 
  setNames(c("x", "y")) %>% 
  as.list %>% 
  c(Population = list(names(V(gnew)))) %>% 
  dplyr::as_data_frame() %>%
  inner_join(pops)
V(gnew)$size <- glayout_df$size
V(gnew)$color <- viridis::viridis(100)[round(100 * (1 - glayout_df$n_private/glayout_df$size))]
gnew <- add_vertices(gnew, length(V(gnew)), size = glayout_df$n_private, color = "grey90")
glayout2 <- rbind(glayout, glayout)
plot(gnew, layout = glayout2)

>>>>

```{r}
library('tidyverse')
library('assertr')
library('poppr')
library('igraph')
library("ggraph")
```

@@

```{r, fig.width = 10, fig.height = 10}
psize <- table(pop(clonecorrect(dat, ~Region)))
pops <- crosses %>%
  mutate_if(is.factor, as.character) %>%
  group_by(Population) %>%
  summarize(MLG = list(as.character(MLG))) %>%
  group_by(Population) %>%
  mutate(size = psize[unlist(Population)]) %>%
  mutate(n_private = size - lengths(MLG)) %>%
  mutate(interactions = list(pg$Population[pg$MLG %in% unlist(MLG)] %>% 
                               setNames(unlist(MLG)) %>% 
                               bind_rows(.id = "MLG") %>% 
                               distinct() %>%
                               filter(Population == from | Population == to))) %>%
  mutate(graph = map(interactions, ~select(.x, from, to, MLG) %>% 
                       rename(name = MLG) %>% 
                       graph_from_data_frame(directed = FALSE)))
pops

possible_edges <- expand.grid(from = pops$Population, to = pops$Population)
possible_edges$Population <- possible_edges$from
from_edges <- right_join(possible_edges, select(pops, Population, size)) %>% 
  tbl_df %>% 
  rename(from_size = size) %>%
  select(-Population)
to_edges <- right_join(mutate(possible_edges, Population = to), select(pops, Population, size)) %>% 
  tbl_df %>% 
  rename(to_size = size) %>%
  select(-Population)

possible_edges <- inner_join(from_edges, to_edges)

par(mfrow = c(3, 4))

@@

glayout_df <- glayout %>% 
  data.frame %>% 
  setNames(c("x", "y")) %>% 
  as.list %>% 
  c(Population = list(names(V(gnew)))) %>% 
  dplyr::as_data_frame() %>%
  inner_join(pops)
V(gnew)$size <- glayout_df$size
V(gnew)$weight <- (1 - glayout_df$n_private/glayout_df$size)
V(gnew)$color <- viridis::viridis(100)[round(V(gnew)$weight * 100)]
gnew <- add_vertices(gnew, length(V(gnew)), size = glayout_df$n_private, color = "grey90")
glayout2 <- rbind(glayout, glayout)
plot(gnew, layout = glayout2)

caps <- as_data_frame(gnew, what = "edges") %>% select(from, to) %>% 
  inner_join(possible_edges) %>% tbl_df

caps %>% mutate(from_size = scale(from_size, center = FALSE)/10) %>%
  mutate(to_size = scale(to_size, center = FALSE)/10) -> spac

glay <- create_layout(gnew, "manual", node.positions = as.data.frame(glayout2) %>% setNames(c("x", "y")))
ggraph(glay) +
  geom_node_circle(aes(r = scale(size, center = FALSE)/10, fill = size, alpha = 1 - weight)) +
  geom_edge_fan() +
  # geom_edge_fan2(aes(start_cap = circle(rep(spac$from_size, 2)/2, "mm"),
  #                   end_cap = circle(rep(spac$to_size, 2)/2, "mm"))) +
  geom_node_label(aes(label = name), repel = TRUE) +
  viridis::scale_fill_viridis(option = "C") +
  coord_fixed() +
  theme_void() +
  labs(list(
    title = "Shared haplotypes across regions",
    fill = "Number of\nGenotypes",
    alpha = "Fraction of private genotpes",
    caption = "Outer circle: Number of genotypes in the region\nInner Circle: Number of private genotypes in the region"
  ))
```
